Formalization of Abstract Rewriting

### 2025-02-23 Relations/Paper/Definitions.tex
Pre call upload

For the rest of this section, let $A$ be a fixed set, and $R$ be a relation on $A$.
(In the Agda code supplement, this is represented by a type $A : \bset$,
and a binary type family $R : A \to A \to \bset$.)

@@

\subsection{Confluence (\texttt{ARS-Properties.agda})}
\begin{definition} The following definitions relate to confluence. Let $A$ and $R$ be as above, and let $a \in A$.
    \begin{description}
        \item[$a \in \WCR_R$] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
        \item[$a \in \CR_R$] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
        \item[$a \in \NPe_R$] \emph{$a$ has the equivalence normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
        \item[$a \in \NP_R$] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$. 
        \item[$a \in \UN_R$] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
        \item[$a \in \UNto_R$] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
    \end{description}
\end{definition}
For each of the subsets defined above we denote in bold face the proposition that the subset contains all of $A$.
That is, for $\mathrm{X} \in \{\WCR , \CR , \NP , \UN \}$ we write $\mathbf{X}$ for the statement that $x \in \mathrm{X}_R$ for all $x \in A$.

In \terese $\NF$ is used to denote $\NPe$, whereas we have chosen to use $\NF$ to denote normal form. Moreover, ${\gNP}$ and ${\gNPe}$ are equivalent when

\begin{proposition}
    $\NPe \leftrightarrow \NP$ 
\end{proposition}
\begin{proof}
    See, \verb|NP₌↔NP : R isNP₌ ↔ R isNP| in \texttt{ARS-Implications.agda}.
\end{proof}
\begin{proposition}
    $\UN \implies \UNto $
\end{proposition}
\begin{proof}
    See, \verb|UN→UN→ : R isUN → R isUN→| in \texttt{ARS-Implications.agda}
\end{proof}
The implication $\UNto \implies \UN$ does not hold, as can be seen in CE-\ref{CE:un} in Subsection \ref{subsec:counterexamples}.
\subsection{Sequences and Recurrence (\texttt{ARS-Properties.agda}, \texttt{Seq.agda})}
The following definitions are key to formalizing Theorem 1.2.3 in \terese.
$R \models \mathbf{X}$ is $\forall a. a \in \mathrm{X}_R$. When $R$ is clear from the context, we will write $\gNP$ for $R \models \gNP$, etc. \sacomment{Mention this earlier}

\begin{definition}
    \begin{description}
        \item[$R \models Inc$] \emph{$R$ is increasing} if there exists a ``size function'' $|-| : A \to \nat$ satisfying, for all $a, b \in A$,
        $Rab \to |a| < |b|$  
    \end{description}
\end{definition}

\sacomment{motivate here going from above defn to the following.}

\begin{definition} Let $A$ and $R$ be as above, and let $a \in A$.
    \begin{description}
        \item[$s : \nat \to A$] \emph{A sequence $s \in A$} is a function from the natural numbers to $A$.  
        \item[$s \in R-increasing$] \emph{A sequence $s \in A$ is $R$-increasing} if every term is $R$-related to its preceding term.
        \item[$a$ is an $s$-bound] if $s (i) \mstep a$ for all $i \in \nat$. 
        \item[$a \in \BP_R$] if all $R$-increasing sequence $s$ with $s (0) = a$ there exists an $s$-bound. 
        \item[$R \models \RPm$] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
        \item[$R \models \RP$] \emph{$R$ has the recurrence property} if every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that 
        $s (i) \in \MF$.
    \end{description}
\end{definition}

The following is immediate.
\begin{proposition}\hfill 
    \begin{enumerate}
        \item $\Inc \implies \RPm$
        \item $\RPm \implies \RP$
    \end{enumerate}
\end{proposition}

@@

\sacomment{tidy up below on rp iff rp- .}
We investigated $\RP$ and thought that with $\RPm$ we had a candidate for a weaker definition that 
did not rely on the notion of $\MF$. We were able to proove that this weaker definition is 
in fact an equivalent definition in the following proof in Agda:

\verb|RP-↔RP : R is RP- ↔ R is RP| \footnotemark[1]

\footnotetext[1]{\texttt{ARS-implications.agda}}
\subsection{Finitely branching}
\sacomment{This property is what makes a lot of the classical properties valid which otherwise wouldn't be. Valid in most interesting rewriting systems. Most 
programming languages will satisfy finite branching.}
\begin{definition}
    \begin{description}
        \item[TODO] TODO 
    \end{description}
\end{definition}
\sacomment{Anything else to define such as finitely branching?}

>>>>

For the rest of this section, let $A$ be a fixed set, and $R$ be a relation on $A$.

@@

\subsection{Confluence (\texttt{ARS-Properties.agda})}
\begin{definition} The following definitions relate to confluence. Let $A$ and $R$ be as above, and let $a \in A$.
    \begin{description}
        \item[$a \in \WCR_R$] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
        \item[$a \in \CR_R$] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
        \item[$a \in \CRs_R$] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
        \item[$a \in \NPe_R$] \emph{$a$ has the equivalence normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
        \item[$a \in \NP_R$] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$. 
        \item[$a \in \UN_R$] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
        \item[$a \in \UNto_R$] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
    \end{description}
\end{definition}
For each of the subsets defined above we denote in bold face the proposition that the subset contains all of $A$.
That is, for $\mathrm{X} \in \{\WCR , \CR , \NP , \UN \}$ we write $\mathbf{X}$ for the statement that $x \in \mathrm{X}_R$ for all $x \in A$.

In \terese $\NF$ is used to denote $\NPe$, whereas we have chosen to use $\NF$ to denote normal form.

\begin{proposition}\hfill 
    \begin{enumerate}
        \item $\gNP \iff \gNPe$ 
        \item $\gUN \implies \gUNto$
    \end{enumerate}
\end{proposition}
\begin{proof} \hfill
    \begin{enumerate}
        \item \verb|NP₌↔NP : R isNP₌ ↔ R isNP| in \texttt{ARS-Implications.agda}.
        \item \verb|UN→UN→ : R isUN → R isUN→| in \texttt{ARS-Implications.agda}. 
    \end{enumerate} 
\end{proof}

The implication $\UNto \implies \UN$ does not hold, as can be seen in Example \ref{CE:un} in Subsection \ref{subsec:counterexamples}.

\subsection{Sequences and Recurrence (\texttt{ARS-Properties.agda}, \texttt{Seq.agda})}
The following definitions are key to formalizing Theorem 1.2.3 in \terese.

\begin{notation}
    $R \models \mathbf{X}$ is $\forall a.\; a \in \mathrm{X}_R$. When $R$ is clear from the context, we will write $\gNP$ for $R \models \gNP$, etc. 
\end{notation}

\begin{definition}
    \begin{description}
        \item[$R \models Inc$] \emph{$R$ is increasing} if there exists a ``size function'' $|-| : A \to \nat$ satisfying, for all $a, b \in A$,
        $Rab \to |a| < |b|$  
        \item[$a \in \CP$] \sacomment{Need a definition of cofinality here}
    \end{description}
\end{definition}

Having a "size function" that maps to the natural numbers is computationally taxing to satisfy. 
Futher, it takes us outside of pure relational theory. The following definitions are for properties which allow us to forgo $\Inc$, for further discussion see Subsection \ref{subsec:def}.
\begin{definition} \label{def:rp} Let $A$ and $R$ be as above, and let $a \in A$.
    \begin{description} 
        \item[$s : \nat \to A$] \emph{A sequence $s \in A$} is a function from the natural numbers to $A$.  
        \item[$s \in R-increasing$] \emph{A sequence $s \in A$ is $R$-increasing} if every term is $R$-related to its preceding term.
        \item[$a$ is an $s$-bound] if $s (i) \mstep a$ for all $i \in \nat$. 
        \item[$a \in \BP_R$] if all $R$-increasing sequence $s$ with $s (0) = a$ there exists an $s$-bound.  
        \item[$R \models \RPm$] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
        \item[$R \models \RP$] \emph{$R$ has the recurrence property} if every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that 
        $s (i) \in \MF$. See Definition \ref{def:mf}. 
    \end{description}
\end{definition}
In \terese $\mathsf{Ind}$ is used to denote $\BP$.

The following is immediate.
\begin{proposition}\hfill 
    \begin{enumerate}
        \item $\gInc \implies \gRPm$
        \item $\gRPm \implies \gRP$
    \end{enumerate}
\end{proposition}

@@

We investigated $\RP$ and thought that with $\RPm$ we had a candidate for a weaker definition that 
did not rely on the notion of $\MF$. We show that this weaker definition is 
in fact an equivalent definition in the following proof in \texttt{ARS-Implications.agda}:

\verb|RP-↔RP : R is RP- ↔ R is RP|.

\subsection{Finitely branching (\texttt{FinitelyBranching.agda})}
\sacomment{This property is what makes a lot of the classical properties valid which otherwise wouldn't be. Valid in most interesting rewriting systems. Most 
programming languages will satisfy finite branching.}
\begin{definition} Let $A$ and $R$ be as above, and let $a \in A$.
    \begin{description}
        \item[$a \in \FB$] \emph{$a$ is finitely branching} if there is a finite amount of  $b \in A$ such that $a \rstep b$. 
    \end{description}
\end{definition}

### 2025-02-23 Relations/Paper/Formalization.tex
Pre call upload

\subsection{Formalization of Definitions}
We have formalized those definitions which were necessary for the formalization of the propositions and theorems found 
in Chapter 1 of \terese. We use Agda's built-in \texttt{Set} for sets and define a relation in \texttt{Predicates.agda}.
The closure operators are formalized in \texttt{ARS-Closure.agda}. 
The definitions given in \terese in \texttt{1.1.8 DEFINITION (confluence)} 
are formalized in \texttt{ARS-Base.agda}. We only cover $\WCR$ and $\CR$ of the definitions from this section 
as the other definitions were not involved in the more interesting formalizations.

The definitions given in \terese in \texttt{1.1.13 DEFINITION (normalization)} 
are formalized in \texttt{ARS-Properties.agda}.

The following is a summary of the differences in definition we have used as mentioned in Section \ref{sec:Definitions}. 
\begin{description}
    \item[$\SN$] We make use of the well-founded defintion, rather than the finite reduction sequence definition.
    \item[$\NPe$] We use the equivalent $\NP$ definition. 
    \item[$\Inc$] We use the more general property $\RP$.      
\end{description}

Our motivation for using $\RP$ rather than $\Inc$ is that we found $\Inc$ to be a particularly difficult property 
to use in a constructive setting. \sacomment{Say more on this motivation and decide where it will be placed.}

@@

\subsection{Theorems}
\subsubsection{Newman's Lemma}
There are three proofs of Newman's Lemma ($\SN \land \WCR \implies \CR$) given in \terese. 
The first and third of these proofs make use of classical properties,

Three proofs are given in \terese of Newman's Lemma (Theorem 1.2.1). The first and third of 
these proofs we found to rely on classical principles. The second proof was amenablbe to a 
constructive formalization which we carried out in the function

\verb|NewmansLemma : R isSN → R isWCR → R isCR| \footnotemark[2]
\footnotetext[2]{\texttt{ARS-NewmansLemma.agda}}
We show in section \ref{sec:Implications} that $\SN$ implies $\SM$, and it is from this implication 
that we produce a new generalization of Newman's lemma. Every relation with the properties 
$\SM$ and $\WCR$ has the property of $\CR$. This holds true both locally and globally as we show in:

\verb|LocalNewmansLemmaRecurrent : R isWCR → SM ⊆ CR| \footnotemark[2]

and \verb|GlobalNewmansLemmaRecurrent : R isWCR → R isSM → R isCR| \footnotemark[2]

The formalization of the proof that $\WCR \land \WN \land \Inc \implies \SN$ proved particularly difficult. 
As already mentioned, we substituted out the property $\Inc$ for the property $\RP$ however 
we found that we still require a classical principle in order for the proof to hold (as can be seen in the type of our proof):
\verb|iii : R isWN → R isWCR → R isRP- → dec (SN) → R isSN| \footnotemark[3] \footnotetext[3]{\texttt{ARS-Theorems.agda}}
The classical property $\decSN$ is a property that states it is decidable whether a given 
element has the property of being $\SN$. \sacomment{Should say more on this proof.}

In the next section we take a closer look at the properties we found most crucial for termination and confluence, and the interrelationship between them.

>>>>

\subsection{Formalization of Definitions}\label{subsec:def}
We have formalized those definitions which were necessary for the formalization of the propositions and theorems found 
in Chapter 1 of \terese. 
The closure operators are formalized in \texttt{ARS-Closure.agda}. 
The definitions grouped as confluent \terese are formalized in \texttt{ARS-Base.agda}. 
The definitions grouped as normalizing in \terese are formalized in \texttt{ARS-Properties.agda}.

The following is a summary of the differences in definition we have used as mentioned in Section \ref{sec:Definitions}. 
\begin{itemize}
    \item $\SN$ : We make use of the well-founded defintion, rather than the finite reduction sequence definition.
    \item $\NPe$ : We use the equivalent $\NP$ definition. 
    \item $\Inc$ : We use the more general property $\RP$.      
\end{itemize}

As already mentioned, the $\Inc$ property was one we wanted to move away from. We saw that $\Inc$ was being used only in Theorem 1.2.3 
and that the crucial facet of $\Inc$ for the proof of the theorem was that every sequence has a bound \sacomment{is this the correct characterization?}. 
So we established that the properties in Definition \ref{def:rp} were sufficient for the proving the theorems. This in turn led us to examining 
a generalization of a normal form, the minimal form. We explore this further in Section \ref{sec:Implications}.

@@

\subsection{Theorems}
\subsubsection{Newman's Lemma}
There are three proofs of Newman's Lemma ($\SN \land \WCR \implies \CR$) given in \terese. 
The first and third of these proofs make use of classical properties. The second proof is amenable to a 
constructive formalization as shown in the following function in \texttt{ARS-NewmansLemma.agda}:

\verb|NewmansLemma : R isSN → R isWCR → R isCR|.

\sacomment{This is a point where it may be useful to examine MF earlier. However, the alternative is to discuss the generalization of NL in the section on implications.}

We show in Section \ref{sec:Implications} a generalization of Newman's Lemma. \sacomment{Delete this comment when that generalization is written.}

The formalizations of the remaining theorems are all found in \texttt{ARS-Theorems.agda}. 
\subsubsection{Theorem 1.2.2}
There are three parts to this theorem. 
\begin{description}
    \item[($i$)] $\gCR \implies \gNPe \implies \gUN$
    \item[($ii$)] $\gWN \land \gUN \implies \gCR$  
    \item[($iii$)] $\gCRs \implies \gCR$
\end{description}

($i$) is formalized in:
\begin{itemize}
    \item \verb|CR→NP : R isCR → R isNP₌|
    \item \verb|NP→UN : R isNP₌ → R isUN|
    \item \verb|CP→UN : R isCR → R isUN|
\end{itemize}

($ii$) is formalized in:
\begin{itemize}
    \item \verb|ii : R isWN × R isUN → R isCR|
\end{itemize}
In our formalization we show that $\gWN \land \gUNto \implies \gCR$ is true and so provide a generalization of ($ii$) as $\gUN \implies \gUNto$.

($iii$) is formalized in:
\begin{itemize}
    \item \verb|iii : subcommutative R → R isCR|
\end{itemize}

\subsubsection{Theorem 1.2.3}
There are four parts to this theorem. 
\begin{description}
    \item[($i$)] $\gWN \and \gUN \implies \gBP$
    \item[($ii$)] $\gBP \land \gInc \implies \gSN$  
    \item[($iii$)] $\gWCR \land \gWN \land \gInc \implies \gSN$
    \item[($iv$)] $\gCR \iff \gCR$ ($\implies$ only holds if the ARS is countable.)
\end{description}
($i$) is formalized in: 
\begin{itemize}
    \item \verb|i : R isWN → R isUN → R isBP|
    \item \verb|i→ : R isWN → R isUN→ → R isBP|
\end{itemize}
In $\mathtt{i\to}$ we again provide a generalization by using $\gUNto$ rather than $\gUN$.

A near formalization of ($ii$) is provided in: 
\begin{itemize}
    \item \verb|iiSeq : R isWN → R isUN → R isRP → isWFseq- (~R R)|
\end{itemize}
\sacomment{Explain here why have we provided a near formalization rather than sticking to the same properties}

($iii$) is formalized in: 
\begin{itemize}
    \item \verb|iii : R isWN → R isWCR → R isRP- → dec (SN) → R isSN|
\end{itemize}
As can be seen we have substituted $\gInc$ with $\gRPm$ which generalizes this theorem. We have also included the assumption that $\gSN$ 
is decidable \sacomment{Is decidability being discussed elsewhere in the paper that we can reference here.} as this property enables us 
to construct a witness for an element that either does or does not have the property $\SN$. Such a witness was necessary for our proof. \sacomment{More to say on this theorem?}

The reverse implication of ($iv$) is formalized in: 
\begin{itemize}
    \item \verb|iv : R isCP → R isCR|
\end{itemize}
We did not formalize $\gCR \to gCP$ as it requires the ARS to be countable \sacomment{More to say?}.

### 2025-02-23 Relations/Paper/Implications.tex
Pre call upload

From the perspective of programming language theory, the two properties of abstract rewriting 
systems that are most interesting are $\SN$ and $\CR$. The following hierarchies 
show chains of implications starting from these properties.

\begin{definition} The folowing definitions relate to being minimal. Let $A$ and $R$ be as above, and let $a \in A$.
    \begin{description}
        \item[$a \in \MF_R$] \emph{$a$ is a minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
        \item[$a \in \WM_R$] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
        \item[$a \in \SM_R$]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is also strongly minimalizing.
        \item[$a \in \MP_R$] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.

@@

Again, we found that there was a strong interrelationship between the properties, captured in Figure \ref{fig:conf-hierarchy}, which are explored in Section \ref{sec:Implications}.

\begin{figure}[h] 
    \centering

          \end{tikzpicture}
          \caption{A hierarchy of confluent properties.}
          \label{fig:conf-hierarchy}

\end{figure}
We found that there was a strong interrelationship between the normalizing properties and the minimal properties. This relationship is 
captured in Figure \ref{fig:norm-hierarchy}.

\begin{figure}[h]   
    \centering
        \begin{tikzpicture}[auto,
            arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
            % A box style
            \tikzstyle{boxnode} = [draw, rectangle, text centered,minimum width=1.2cm, inner sep=3pt]   
            % Define the nodes
            \node (SN) [boxnode] at (4,0) {$\SN$};
            \node (WN) [boxnode, above right=0.5cm and 0.5cm of SN] {$\WN$};
            \node (SR) [boxnode, below right=0.5cm and 0.5cm of SN] {$\SM$};
            \node (WR) [boxnode, below right=0.5cm and 0.5cm of WN] {$\WM$};

            % Draw the arrows to form a diamond
            \draw [arrowstyle] (SN) -- (WN);
            \draw [arrowstyle] (SN) -- (SR);
            \draw [arrowstyle] (WN) -- (WR);
            \draw [arrowstyle] (SR) -- (WR);
        \end{tikzpicture}
        \caption{A hierarchy of normalizing and minimal properties.}
        \label{fig:norm-hierarchy}
\end{figure}

The implications will be explored in detail in Section \ref{sec:Implications}.

Proposition \ref{prop:SMRP} connects $\SM$ with $\RP$ and $\BP$. \sacomment{Need to relate SM and SMseq. Probably define SMseq and metion 
we can only prove this for SMseq.}
\begin{proposition}\label{prop:SMRP}
    $SM \leftrightarrow RP \land BP$
\end{proposition}
\begin{proof}
    See,\\ \verb|RP∧BP→SMseq : R isRP → R isBP → ∀ {x : A} → SMseq R x| \\ \verb|RisSMseq→RisRP : (∀ {x : A} → SMseq R x) → R isRP|
    \\ \verb|RisSMseq→RisBP : (∀ {x : A} → SMseq R x) → R isBP| in \texttt{ARS-Implications.agda}.
\end{proof}

A trivial implication not captured in the above figure is covered in Proposition \ref{prop:nftomf}. 
\begin{proposition}\label{prop:nftomf}
    $a\in NF_R \implies a \in MF_R$ 
\end{proposition}    
\begin{proof}
    See, \verb|NF ⊆ MF : ∀x → NFx → MFx| in \texttt{ARS-Implications.agda}.
\end{proof}

@@

        % Define the nodes
        \node (SN) [boxnode] at (4,0) {$\SN$};
        \node (WN) [boxnode, above right=0.5cm and 0.5cm of SN] {$\WN$};
        \node (SR) [boxnode, below right=0.5cm and 0.5cm of SN] {$\SM$};
        \node (WR) [boxnode, below right=0.5cm and 0.5cm of WN] {$\WM$};

        % Draw the arrows to form a diamond
        \draw [arrowstyle] (SN) -- (WN);
        \draw [arrowstyle] (SN) -- (SR);
        \draw [arrowstyle] (WN) -- (WR);
        \draw [arrowstyle] (SR) -- (WR);
      \end{tikzpicture}
\end{center}

The classical property of being minimally decidable is required to complete the implcation 
from $\SN$ to $\WN$, as can be seen in our formalization

\verb|SNdec→WN : (~R R) isMinDec → SN ⊆ WN| \footnotemark[1]

@@

The following tables show which combination of these properties implies a property higher in the hierarchy. Where a combination 
does not imply a higher property an explanatory counterexample is given. The counterexamples referenced are shown below the tables in subsection \ref{subsec:counterexamples}.

The first table explores where the properties hold locally, the second explores where the properties hold globally. The proofs that the 
following implications hold are primarily found in \texttt{ARS-implications.agda} unless they have been proven as part of the formalization 
of \terese, in which case they will be found in either \texttt{ARS-thoerems.agda} or \texttt{ARS-NewmansLemma.agda}.

\sacomment{When the table and CE are finished, write an explanation that the CE to the local table 
assume local WCr and the global table CEs assume global WCR!}
\sacomment{UPDATE COUNTEREXAMPLES WHEN CE SECTION FINISHED}
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\begin{table}[h!]
    \centering
    \caption{Local implications}
    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
    \hline
    \rowcolor{gray!30}     & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
    \hline
    $\UNto$ &  CE-\ref{CE:4}, CE-\ref{CE:12}     & CE-\ref{CE:4}, CE-\ref{CE:7}       & CE-\ref{CE:4} , CE-\ref{CE:9}          & CE-\ref{CE:4}, CE-\ref{CE:4}            & $\CR$\footnotemark[1] , $\SN$ \\
    \hline
    $\NP$ & CE-\ref{CE:10},CE-\ref{CE:9}      & $\CR$, CE-\ref{CE:7}    & CE-\ref{CE:11} , CE-\ref{CE:9}          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\MP$ & $\CR$ , CE-\ref{CE:9}    & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[2] , CE-\ref{CE:9} & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\CR$   & $\CR$, CE-\ref{CE:9}     & $\CR$, CE-\ref{CE:7}     & $\CR$, CE-\ref{CE:9}        & $\CR$, $\SN$     & $\CR$ , $\SN$ \\
    \hline

@@

>>>>

% From the perspective of programming language theory, the two properties of abstract rewriting 
% systems that are most interesting are $\SN$ and $\CR$. The following hierarchies 
% show chains of implications starting from these properties.
As discussed in Subsection \ref{subsec:def} we put forward $\RP$ as an alternative for $\Inc$. It is through examining $\RP$ that 
we came to the below definitions.

\begin{definition}\label{def:mf}  Let $A$ and $R$ be as above, and let $a \in A$.
    \begin{description}
        \item[$a \in \MF_R$] \emph{$a$ is a minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
        \item[$a \in \WM_R$] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
        \item[$a \in \SM_R$]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is also strongly minimalizing.
        \item[$a \in \MP_R$] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.

@@

\sacomment{Need to relate SM and SMseq. Probably define SMseq and metion 
we can only prove this for SMseq.}
\begin{proposition}\label{prop:SMRP}
    $SM \leftrightarrow RP \land BP$
\end{proposition}
\begin{proof}
    See,\\ \verb|RP∧BP→SMseq : R isRP → R isBP → ∀ {x : A} → SMseq R x| \\ \verb|RisSMseq→RisRP : (∀ {x : A} → SMseq R x) → R isRP|
    \\ \verb|RisSMseq→RisBP : (∀ {x : A} → SMseq R x) → R isBP| in \texttt{ARS-Implications.agda}.
\end{proof}

Trivially, the following also holds. 
\begin{proposition}\label{prop:nftomf}
    $a\in NF_R \implies a \in MF_R$ 
\end{proposition}    
\begin{proof}
    See, \verb|NF ⊆ MF : ∀x → NFx → MFx| in \texttt{ARS-Implications.agda}.
\end{proof}

With these minimal definitions we can see the taxonomy of concepts that relate to termination and confluence.

@@

        % Define the nodes
        \node (NF) [boxnode] at (3,0) {$\NF$};
        \node (MF) [boxnode] at (3,-1) {$\MF$};
        \node (SN) [boxnode] at (5,0) {$\SN$};
        \node (SR) [boxnode] at (5,-1) {$\SM$};
        \node (WN) [boxnode] at (7,0) {$\WN$};
        \node (WR) [boxnode] at (7,-1) {$\WM$};

        % Draw the arrows to form a diamond
        \draw [arrowstyle] (NF) -- (SN);
        \draw [arrowstyle] (NF) -- (MF);
        \draw [arrowstyle] (MF) -- (SR);
        \draw [arrowstyle] (SN) -- (WN);
        \draw [arrowstyle] (SN) -- (SR);
        \draw [arrowstyle] (WN) -- (WR);
        \draw [arrowstyle] (SR) -- (WR);
      \end{tikzpicture}
\end{center}

The implications in this diagram are formalized in \texttt{ARS-Implications.agda}. The classical property of being minimally decidable is 
required to complete the implcation from $\SN$ to $\WN$, as can be seen in our formalization

\verb|SNdec→WN : (~R R) isMinDec → SN ⊆ WN|

@@

We are interested in seeing which combination of properties a relation requires in order to be complete (that is, $\CR$ and $\SN$). 
The following tables show either that a given combination is complete, or the appropriate counterexample which demonstrates why 
those properties do not provide a property higher on the taxonomical hierarchy.

The first table explores where the properties hold locally, the second explores where the properties hold globally. Counterexamples in the 
first table assume $\WCR$ and in the second table assume $\gWCR$.

\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\begin{table}[h!]
    \centering
    \caption{Local implications}
    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
    \hline
    \rowcolor{gray!30}     & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
    \hline
    $\UNto$ &  CE-\ref{CE:4}, CE-\ref{CE:12}     & CE-\ref{CE:4}, CE-\ref{CE:7}       & CE-\ref{CE:4} , CE-\ref{CE:9}          & CE-\ref{CE:4}, CE-\ref{CE:4}            & $\CR$\footnotemark[1] , $\SN$ \\
    \hline
    $\NP$ & CE-\ref{CE:10},CE-\ref{CE:9}      & $\CR$, CE-\ref{CE:7}    & CE-\ref{CE:11} , CE-\ref{CE:9}          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\MP$ & $\CR$ , CE-\ref{CE:9}    & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[2] , CE-\ref{CE:9} & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\CR$   & $\CR$, CE-\ref{CE:9}     & $\CR$, CE-\ref{CE:7}     & $\CR$, CE-\ref{CE:9}        & $\CR$, $\SN$     & $\CR$ , $\SN$ \\
    \hline

@@

that $\SN$ implies $\SM$, and it is from this implication 
that we produce a new generalization of Newman's lemma. Every relation with the properties 
$\SM$ and $\WCR$ has the property of $\CR$. This holds true both locally and globally as we show in:

\verb|LocalNewmansLemmaRecurrent : R isWCR → SM ⊆ CR| \footnotemark[2]

and \verb|GlobalNewmansLemmaRecurrent : R isWCR → R isSM → R isCR| \footnotemark[2]

\sacomment{We should remember that If global WCR and local SM implies local CR, then if we also have local WN, we get local SN.}
